NumPy---Array Programming in Python

### 2020-01-31 body.tex
Cleanup

Other array-aware functions, such as \code{maximum}, perform
element-by-element \emph{reductions}, aggregating results across one,
multiple, or all axes of a single array.
For example, summing an $n$-dimensional array over $d$ axes results in a
$(n-d)$-dimensional array (Fig.~\ref{fig:array-concepts}e).

@@

NumPy suits most user's needs, but it cannot support every specialized need
of the community; due to its in-memory data model, it is limited in its ability
to work with very large datasets, datasets split across multiple systems, and
computations that require graphics processing units (GPUs), tensor processing
units (TPUs) or other specialized hardware for performance reasons.
However, both distributed data and the parallel execution of GPUs and TPUs
map well to the paradigm of array orientated programming.
This leads to a gap between available modern hardware architecture and the
necessary tools to leverage their computational power.

@@

\emph{Python} is an open source, general-purpose, interpreted programming language
well-suited to standard programming tasks such as cleaning data,
interacting with web resources, and parsing text.
Adding fast array operations and linear algebra allows scientist to do all
their work within a single language---and one that has the advantage of
being famously easy to learn and teach.
In fact, Python's adoption as a primary learning language in universities
(e.g., many lower division UC Berkeley courses use Python including
Foundations of Data Science,
The Beauty and Joy of Computing,
Introduction to Computational Thinking with Data,
and The Structure and Interpretation of Computer Programs) has
further popularized NumPy as a tool of choice for modern data science.

>>>>

Other array-aware functions, such as \code{sum}, \code{mean}, and \code{maximum}, perform
element-by-element \emph{reductions}, aggregating results across one,
multiple, or all axes of a single array.
For example, summing an $n$-dimensional array over $d$ axes results in a
$(n-d)$-dimensional array (Fig.~\ref{fig:array-concepts}e).

@@

NumPy suits most user's needs, but it cannot support every specialized need
of the community; due to its in-memory data model, it is limited in its ability
to work with very large datasets, datasets split across multiple systems, and
computations that require graphics processing units (GPUs), tensor processing
units (TPUs) or other specialized hardware for performance reasons.
However, both distributed data and the parallel execution of GPUs and TPUs
map well to the paradigm of array programming.
This leads to a gap between available modern hardware architecture and the
necessary tools to leverage their computational power.

@@

\emph{Python} is an open source, general-purpose, interpreted programming language
well-suited to standard programming tasks such as cleaning data,
interacting with web resources, and parsing text.
Adding fast array operations and linear algebra allows scientist to do all
their work within a single language---and one that has the advantage of
being famously easy to learn and teach.
In fact, Python's adoption as a primary learning language in universities
has further popularized NumPy as a tool of choice for modern data science.
